\pagenumbering{arabic}

\section{Introduction}

	Medicine today is highly advanced and is able to treat an immense amount of diseases and disorders.
	This results in high standards and a lot of pressure on people working in this branch. In order to further improve the standards this amount of errors has to be 		minimized, since they can have fatal consequences.

	In pursuance of achieving, maintaining as well as improving these abilities, technological assistance is of utmost importance.\\  

	Since the brain is one of the main organs, caution and accuracy is essential while treating its conditions. 
	%Umformulieren?
	Techniques such as the MEG (Magnetoencephalography) or EEG (Electroencephalography) observe the brains activity by 				measuring and monitoring magnetic fields or electrical deviations.

	These procedures help diagnosing epilepsy, brain death and other severe brain diseases.

	Furthermore they are used for research in fields like psychology.
	A proper visualization aids the usability of the generated data. \\

	The MNE-CPP  project builds tools for the purpose of making analyzing EEG and MEG data easier.
	Thus the whole project is open-source and everyone can contribute. As language only C++ is used, although the project 			simultaneously exists in other languages, e.g. Python. %Nur Python?
	MNE-Scan, -Analyze and -Browse are some of the features of the existing framework. \\

	The new extension of the current project and focuses on real-time 3D-visualization of EEG/MEG sensor date, while being as 		exact and fast as possible. It is integrated into the existing code and accessible through the MNE-Client as well as 			compatible with operating systems Linux and Windows.
  
