\section{Glossary}

\begin{aims}
	
	\item[MNE-CPP] is a cross-platform C++ framework that provides MEG/EEG tools and applications for fast non-invasive brain 						monitoring.
	\item[MEG] stands for Magnetoencephalography. 
	\item[EEG] stands for Electroencephalography.
	\item[Vertex] is a point where two or more lines or edges meet.
	\item[Mesh]	contains a number of vertices and edges, forming a 3D shape. Often these vertices and edges are structured as 					triangles.
	\item[Euclidian Distance] is the shortest distance between two points in a 3D space.
	\item[SCDC]stands for surface constrained distance calculation. A shortest path between two points on a tessellated 					   surface is determined.
	\item[Interpolation] is the mathematical process of determining the value of a function between two points at which it has 						 prescribed values.
	\item[Bad Channels] are sensor inputs that do not deliver working signals or are not set up correctly.
	\item[CPU] (central processing unit) is alternately referred to as processor and is the computer component 				   			   that is responsible for interpreting and executing most of the commands from other hardware and software.
	\item[GPU] (grapics processing unit) is a programmable logic chip specialized for display functions. It renders images, 				   animations and videos for the computer's screen. 	
	\item[GPU-Level] is a term for using the GPU (possibly instead of the CPU) to do calculations.
	\item[Shaders] are used in 3D computer graphic calculations. A shader is a small program or set of algorithms that 							   determines how 3D surface properties of objects are rendered, and how light interacts with the object. 		
	\item[Compute Shaders] are a shader type in OpenGL and Direct3D. They can execute calculations outside the typical 									   rendering pipeline, thus making parallelization possible.
	\item[Qt] is a cross-platform framework, mainly used for software applications and graphical user interfaces (GUIs). 
	\item[Eigen] is a library that provides mathematical functions for programming.
	\item[Efficiency] describes an economical usage of resources. Low storage consumption and small GPU workload are optimal 					  	  for the system.
	\item[Sturdiness] is the ability of the system to function properly and without failures even under non-optimal 								  circumstances. 
	\item[Reliability] measures the possibility of wrong output or total failure of the system.
	\item[Security] describes how easily a software can be manipulated.
	\item[Portability] is the ability of software to be ported from one system to another.

\end{aims}