\subsection {Glossary}

\item [Bad channels] are sensor inputs that do not deliver working signals or are not set up correctly.
\item [Compute shaders] are a shader type in OpenGL and Direct3D. they can execute calculations outside the typical rendering pipeline, making parallelization possible.
\item [Disp3D]
\item [Eigen] is a library that provides mathematical functions for programming.
\item [Fibonacci Heap] is a data structure for priority queue operations, consisting of a collection of heap-ordered trees.
\item [GPU] (graphics processing unit) is a programmable logic chip specialized for display functions.
\item [GUI] (graphical user interface) is a type of user interface that allows users to interact with electronic devices through graphical icons and visual indicators such as secondary notation.
\item [Linear search] or sequential search is a method for finding a target value within a list.
\item [MNE-CPP] is a cross-platform C++ framework, which provides MEG/EEG tools and applications for fast non-invasive brain monitoring.
\item [OpenGL] is a cross-language, cross-platform application programming interface (API) for rendering 2D and 3D vector graphics.
\item [Qt] is a cross-platform framework, mainly used for software applications and graphical user interfaces.
\item [SCDC] (surface constrained distance calculation) determines the shortest path between two points on a tessellated surface.
\item [UML] (unified modeling language)  is a modeling language that is intended to provide a standard way to visualize the design of a system. 
